EEG Waveform Analysis of P300 ERP with applications to Brain Computer Interfaces

### 2018-11-07 BrainScience/brainscience.tex
Adding modifications per Reviewers comments

The problem with any P300 experiment is that users are part of a closed loop with the BCI system and the human is typically considered as a static compliant entity that always performs what the experimenter asks for in a precise and consistent way.  Therefore, P300 experiments are often mined with null-signals.  These are EEG streams which are marked as hit but, because the subject was not particularly focused, or concentrated or so on, the real signal is not generated.   This lack of certainty may be in detriment of analysis of algorithms and can be misleading.   Similar experiments had address this same issue, particularly when benchmarking different algorithms.

>>>>

The problem with any P300 experiment is that users are part of a closed loop with the BCI system and the human is typically considered as a static compliant entity that always performs what the experimenter asks for in a precise and consistent way~\citep{Chavarriaga2017}.  Therefore, P300 experiments are often mined with null-signals.  These are EEG streams which are marked as hit but, because the subject was not particularly focused, or concentrated or so on, the real signal is not generated.   This lack of certainty may be in detriment of analysis of algorithms and can be misleading.   Similar experiments had address this same issue, particularly when benchmarking different algorithms.
